---
title: "Untitled"
date: "MM/DD/YYYY"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
knit: (function(i, encoding) {apstyle::render(i, encoding)})
---
<!-- Timestamp: leave this in to automatically track when a file is rendered -->
*Rendered at `r format(Sys.time(), '%I:%M %p, %b. %d, %Y')`*

<!-- Contact info: leave author/reporter/editor contact info here -->
*Firstname Lastname (<email@domain.com>)*

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
  )

knitr::opts_knit$set(
  root.dir = rprojroot::find_rstudio_root_file()
  )
```
```{r initialize}
# Load files, environment variables, libraries, etc. here
library(tidyverse)
library(apstyle)
library(readxl)
library(dplyr)  

```

## Overview

```{r}
#load data
excel_files <- list.files(path = "~/Documents/campuscrimeproject/data", pattern = "\\.xlsx$", full.names = TRUE)
unccrime <- purrr::map_dfr(excel_files, read_excel)

#clean data
#look at lubridate
cleanunccrime <- unccrime  %>% 
  separate('Event Date', into = c("Event Start Date", "Event End Date"), sep = " - ", convert = TRUE) %>%
  separate('Event Start Date', into = c("Event Start Date", "Event Start Time"), sep = " ", convert = TRUE) %>%
  separate('Event End Date', into = c("Event End Date", "Event End Time"), sep = " ", convert = TRUE) %>%
  separate('Date Reported', into = c("Date Reported", "Time Reported"), sep = " ", convert = TRUE) %>%
  separate('Event Start Date', into = c("Event Start Month", "Event Start Date", "Event Start Year"), sep = "/", convert = TRUE) %>%
 separate('Event End Date', into = c("Event End Month", "Event End Date", "Event End Year"), sep = "/", convert = TRUE) %>%
 separate('Date Reported', into = c("Month Reported", "Date Reported", "Year Reported"), sep = "/", convert = TRUE)
```


Q1: How have the number of crimes in the past year changed?
```{r}
#may 2023 vs may 2022
may2022 <- cleanunccrime %>%
  filter(`Event Start Year` == 2022, `Event Start Month` == 5) %>%
  group_by(`Event Start Month`, `Event Start Date`) %>%
  summarize(number_of_crimes = n())

plot2022 <- ggplot(may2022, aes(x = `Event Start Date`, y = number_of_crimes)) +
  geom_line()
plot2022
```

Q2: What is the overall trend of accidents in Chapel Hill over the past year, and are there any particular locations or intersections that have consistently recorded a higher number of accidents?
```{r}
#franklin vs columbia/other main unc streets
ch_accidents22 <- cleanunccrime %>%
  filter(`Event Start Year` == 2022, Type == "Accident")

ch_accidents23 <- cleanunccrime %>%
  filter(`Event Start Year` == 2023, Type == "Accident")
```

Q3:How promptly are the Chapel Hill Police Department officers responding to accident reports, as shown by the time difference between the event and reporting dates?
```{r}
#gap bw end of incident and report date

```


## References

<!-- This section is for including references to related material -->

- CREDO National Charter School Study 2013: http://credo.stanford.edu/documents/NCSS%202013%20Final%20Draft.pdf

- NBER Working Paper No. 23947: The Labor Market Effects of Offshoring by U.S. Multinational Firms: Evidence from Changes in Global Tax Policies: http://www.nber.org/papers/w23947

<!-- This section is for a tests code block -->

```{r tests}
# Leave this block of code at the end of the file
# If a test fails it will stop the Rmd document from knitting
# Run tests like so:
# source("tests/etl_test.R")
```
