---
title: "UNC Campus Crime"
date: "MM/DD/YYYY"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
knit: (function(i, encoding) {apstyle::render(i, encoding)})
---
<!-- Timestamp: leave this in to automatically track when a file is rendered -->
*Rendered at `r format(Sys.time(), '%I:%M %p, %b. %d, %Y')`*

<!-- Contact info: leave author/reporter/editor contact info here -->
*Firstname Lastname (<email@domain.com>)*

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
  )

knitr::opts_knit$set(
  root.dir = rprojroot::find_rstudio_root_file()
  )
```
```{r initialize}
# Load files, environment variables, libraries, etc. here
library(tidyverse)
library(apstyle)
library(readxl)
library(dplyr)  
library(lubridate)
library(janitor)
library(tidygeocoder)
library(sf)
library(tigris)
library(crsuggest)
library(ggplot2)
library(leaflet)
```

## Overview

```{r}
#load data
excel_files <- list.files(path = "~/Documents/campuscrimeproject/data", pattern = "\\.xlsx$", full.names = TRUE)
unccrime <- purrr::map_dfr(excel_files, read_excel) %>%
  separate('Event Date', into = c("Event Start Date", "Event End Date"), sep = " - ", convert = TRUE) %>%
  clean_names()

#look at lubridate

```


Q1: How have the number of crimes in the past year changed?
```{r}
#may 2023 vs may 2022

may2022 <- unccrime %>%
  mutate(event_start_date = mdy_hms(event_start_date)) %>%
  filter(year(event_start_date) == 2022, month(event_start_date) == 5) %>%
  group_by(day = date(event_start_date)) %>%
  summarize(number_of_crimes = n())  

may2023 <- unccrime %>%
  mutate(event_start_date = mdy_hms(event_start_date)) %>%
  filter(year(event_start_date) == 2023, month(event_start_date) == 5) %>%
  group_by(day = date(event_start_date)) %>%
  summarize(number_of_crimes = n())  

maycrime <- ggplot() +
  geom_line(data = may2022, aes(x = day(day), y = number_of_crimes, color = "blue")) +
  geom_line(data = may2023, aes(x = day(day), y = number_of_crimes, color = "green")) +
  labs(x = "Dates in May", y = "# of Crimes", title = "Chapel Hill May Crime Trends") +
  scale_x_continuous(breaks = seq(1, 31, by = 1)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_manual(values = c("blue", "green"), labels = c("2022", "2023")) +
  theme_ap(family = "") +
  theme(legend.position = "right")
maycrime

```

Q2: Have there been more accidents on Franklin Street over the past year?
```{r}
#are there more accidents on a certain part of franklin st
franklin_accidents <- unccrime %>%
  mutate(event_start_date = mdy_hms(event_start_date)) %>%
  filter(year(event_start_date) == 2022, month(event_start_date) == 5, str_detect(location, fixed("FRANKLIN", ignore_case = TRUE)))


franklingeocode <- franklin_accidents %>%
  geocode(location, method = 'arcgis', lat = latitude , long = longitude, full_results = TRUE)

franklin_accidents22 <- unccrime %>%
  mutate(event_start_date = mdy_hms(event_start_date)) %>%
  filter(year(event_start_date) == 2023, month(event_start_date) == 5, str_detect(location, fixed("FRANKLIN", ignore_case = TRUE)))


franklingeocode22 <- franklin_accidents22 %>%
  geocode(location, method = 'arcgis', lat = latitude , long = longitude, full_results = TRUE)

leaflet() %>%
    addTiles() %>%
    setView(lng = -79.0561, lat = 35.9111, zoom = 15) %>%
    addCircleMarkers(data = franklingeocode, color = "blue") %>%
    addCircleMarkers(data = franklingeocode22, color = "green")

#clusters

```

Q3: Is there a gap between the end of each incident and the report date for any of these cases?
```{r}
gap_in_data <- unccrime %>%
  mutate(gap_days = difftime(mdy_hms(date_reported), mdy_hms(event_end_date), units = "days"),
         gap_in_data = gap_days > 0) %>%
  select(event_end_date, date_reported, gap_in_data)

cases_with_gaps <- gap_in_data %>%
  filter(gap_in_data == TRUE)

num_cases_with_gaps <- nrow(cases_with_gaps)
num_cases_with_gaps

#calculate average time between event end date and date reported


average_time <- mean(time_diff, na.rm = TRUE)
average_time

gap_greater_average <- unccrime %>%
  mutate(time_between = difftime(mdy_hms(date_reported), mdy_hms(event_end_date), units = "days")) %>%
  filter(time_between > average_time)
gap_greater_average

```


## References

<!-- This section is for including references to related material -->

- CREDO National Charter School Study 2013: http://credo.stanford.edu/documents/NCSS%202013%20Final%20Draft.pdf

- NBER Working Paper No. 23947: The Labor Market Effects of Offshoring by U.S. Multinational Firms: Evidence from Changes in Global Tax Policies: http://www.nber.org/papers/w23947

<!-- This section is for a tests code block -->

```{r tests}
# Leave this block of code at the end of the file
# If a test fails it will stop the Rmd document from knitting
# Run tests like so:
# source("tests/etl_test.R")
```
